A High Efficiency MAC Protocol for WLANs: Providing Fairness in Dense Scenarios

### 2015-10-07 results.tex
More figures modified to comply with the new style

	\begin{figure}[tb]
	\centering
		\includegraphics[width=0.7\linewidth,angle=-90]{figures/saturated/throughput-saturated-w-BOS/throughput-saturated-w-BOS2.eps}
		\caption{Throughput under saturated conditions}
		\label{fig:throughput-sat}
	\end{figure}

	\begin{figure}[tb]
	\centering
		\includegraphics[width=0.7\linewidth,angle=-90]{figures/saturated/collisions-saturated/collisions-saturated.eps}
		\caption{Average percentage of collision slots: the fraction of time slots containing collisions.}
		\label{fig:collisions-sat}
	\end{figure}

	\begin{figure}[tb]
	\centering
		\includegraphics[width=0.7\linewidth,angle=-90]{figures/saturated/slots/Pc-evolution.eps}
		\caption{Evolution of the fraction of collision slots in a scenario with 70 saturated stations.}
		\label{fig:collisions-evolution}
	\end{figure}

@@

	\begin{figure}[tb]
	\centering
		\includegraphics[width=0.7\linewidth,angle=-90]{figures/clockDrift/throughput_and_BOS_w_SD.eps}
		\caption{Throughput when increasing the clock drift probability}
		\label{fig:clockDrift}
	\end{figure}

>>>>

	\begin{figure}[tb]
	\centering
		\includegraphics[width=0.7\linewidth,angle=-90]{figures/saturated/throughput-saturated-w-BOS/throughput-saturated-w-BOS-TON.eps}
		\caption{Throughput under saturated conditions}
		\label{fig:throughput-sat}
	\end{figure}

	\begin{figure}[tb]
	\centering
		\includegraphics[width=0.7\linewidth,angle=-90]{figures/saturated/collisions-saturated/collisions-saturated-TON.eps}
		\caption{Average percentage of collision slots: the fraction of time slots containing collisions.}
		\label{fig:collisions-sat}
	\end{figure}

	\begin{figure}[tb]
	\centering
		\includegraphics[width=0.7\linewidth,angle=-90]{figures/saturated/slots/Pc-evolution-TON.eps}
		\caption{Evolution of the fraction of collision slots in a scenario with 70 saturated stations.}
		\label{fig:collisions-evolution}
	\end{figure}

@@

	\begin{figure}[tb]
	\centering
		\includegraphics[width=0.7\linewidth,angle=-90]{figures/clockDrift/throughput_and_BOS_w_SD-TON.eps}
		\caption{Throughput when increasing the clock drift probability}
		\label{fig:clockDrift}
	\end{figure}
